### 2019-02-12 sections/relatedwork.tex
typo
workflows are like GOTO

As mentioned earlier, iTasks is an implementation of \TOP. iTasks has many
features, and its basic combinators are versatile and powerful.vSimpler
combinators are implemented by restricting the powerful ones. This is useful for
everyday programming, where having lots of functionality at one's fingertips is
convenient and efficient.

@@

Much research has been done into workflow modeling. These works focus on
describing the collaboration between subsystems, rather than the communication
between them.

>>>>

As mentioned earlier, iTasks is an implementation of \TOP. iTasks has many
features, and its basic combinators are versatile and powerful. Simpler
combinators are implemented by restricting the powerful ones. This is useful for
everyday programming, where having lots of functionality at one's fingertips is
convenient and efficient.

@@

Much research has been done into workflow modeling. These works focus on
describing the collaboration between subsystems, rather than the communication
between them.
The systems described here follow a \emph{boxes and arrows} model of specifying workflows.
Control flow, represented by arrows, usually can go unrestricted from anywhere to anywhere else in a workflow.
We see \TOP as the functional programming of workflows, as opposed to this GOTO style.
